Prospects of detecting gamma-ray emission from galaxy clusters: cosmic rays and dark matter annihilations

### 2011-04-08 paper.tex
further editing to App, pop studies

Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray flux with
predictions of DM annihilation fluxes in the leptophilic and benchmark models.
To obtain the $\gamma$-ray fluxes, we scale the virial mass of clusters in the
extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our scaling
relations of Equations~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}).  We
assume a boost factor due to substructures that has a constant contribution per
decade in substructure mass and has a mass spectrum extending down to Earth
masses. Fermi limits rule out the leptophilic models in their present form with
the mentioned assumptions in 14 clusters, and limit the boost from Sommerfeld
enhancement to less than 4 [?] in Fornax. Assuming universality, this limits the
Sommerfeld boost in the MW to less than 10 (see Fig.~\ref{fig:boost_const}).
The flux level of the Fermi limits are an indirect measure of the ambient
background flux in the $\gamma$-ray sky and/or the presence of strong point
sources such as AGN in the immediate vicinity of the cluster position. Hence, the ratio of
the Fermi upper limits to the predicted annihilation fluxes,
$F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good indication of the best cluster
candidates for indirect DM experiments. We identify Fornax, M49, NGC4636, and
Virgo to be prime candidates. Note however, that Virgo extends of $7\deg$ over
the sky which implies a lower surface brightness and lower signal-to-noise.
Fermi limits on individual clusters are expected to improve as $\sqrt{T/1.5
  \mathrm{yr}}$, where $T$ is the total elapsed time of the Fermi mission. We
emphasize that the very inhomogeneous distribution of $F_{\mathrm{UL}}/
F_{\mathrm{scal}}$ makes it unlikely to dramatically improve the limits through
a stacking analysis as the weak signal will dilute the average constraints.
Assuming the projected sensitivity of the future Cherenkov telescope array (CTA)
of [ANDERS: value?], we note that it will be difficult to detect the DM
annihilation signal from clusters without a Sommerfeld boost by Cherenkov
telescopes. This is because the boost from substructures is extended while the
sensitivity of Cherenkov telescopes drops linearly with radius outside the point
spread function.

@@

In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the flux
predictions by the semi-analytical Pinzke and Pfrommer model
\cite{2010MNRAS.409..449P} for CRp induced $\gamma$-rays that uses the
X-ray-inferred density profiles of clusters as an input. For consistency, we use
beta-model fits to ROSAT data of X-ray bright clusters for our $\gamma$-ray flux
estimates \cite{2002ApJ...567..71}). Hence these predictions are superior to
those that use luminosity-mass scaling relation to infer the expected
$\gamma$-ray flux---a method used by reference \cite{2010ApJ...717L..71A} to
compare to Fermi limits.  In this semi-analytic model, we employ the fact that
CRs accelerated at structure formation shocks and transported over cosmic time
exhibit a universal spectral form and an almost universal spatial
distribution. Depending on whether or not we account for the bias of
``artificial galaxies'' in cosmological simulations, we derive an optimistic or
conservative limit of the expected $\gamma$-ray emission from decaying pions
(bracketing our ignorance of the contribution of cluster galaxies to the overall
$\gamma$-ray flux from a cluster). Note that both models assume the maximally
allowed acceleration efficiency for strong shocks that transfer 50\% of the
shock kinetic energy to CRs and most likely will have to be corrected down if
this number is not realized at structure formation shocks. Secondly, these
simulations neglect active CR transport such as streaming and diffusion relative
to the gas, i.e. we assume that advective transport is the dominant one and CRs
are tightly coupled to the gas via flux-frozen magnetic fields tangled on
sufficiently small scales. Evidence from the statistics of radio halos suggests
that this might not be the case for relaxed clusters, arguing that CR streaming
in those objects could be responsible for a decrease in the central CR number
density. This effect would also reduce the expected $\gamma$-ray flux by up to a
factor of five \cite{2011A&A...527A..99E}. We note that the tightest Fermi
limits are obtained in the 1-10 GeV regime due to the largest effective area of
LAT there. In this energy band, the Fermi limits come close to the flux
predictions of Virgo, Coma and Norma. Using integrated flux limits from Fermi,
we arrive at very similar results.  We emphasize that by using our semi-analytic
modeling, the slight discrepancy of the scaling relation-based prediction with
the Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
seems to be less bright than an average cluster of the same mass as Norma. The
insenstitive limit on Perseus comes about since the central AGN in NGC1275 has
turned on over the last years, making it hard to determine a comparable
limit as obtained from teh other clusters.

\begin{figure*}%[t]
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
 \caption{\it Comparison of the gamma-ray flux induced by CRps for the 106
   clusters included in the extended HIFLUGCS catalogue. The fluxes are
   calculated within $\rvir$, and are derived using a single beta profile for
   each cluster's gas density profile as obtained by ROSAT X-ray
   observations. The CR distribution follows the semi-analytically model derived
   by hydrodynamical cosmological cluster simulations \cite{2010MNRAS.409..449P}
   (see text for details). The upper panel shows the energy integrated flux
   above 100~MeV (left side) and above 100~GeV (right side), both as a function
   of HIFLUGCS cluster ID. The eight brightest clusters are labelled. The lower
   panel shows the relative difference between the gamma-ray flux predicted by
   the mass-luminosity scaling relation and to the flux computed using the
   semi-analytical model \cite{2010MNRAS.409..449P}. The name of the clusters
   with the largest offset are printed out, which correlate with cool core
   clusters.}
 \label{fig19}
\end{minipage}
\end{figure*}

@@

\clearpage

@@

\del{
Some of the results (should discuss what we want to emphasize):
O) the flux from annihilating DM is boosted by about a factor 1000 in
 clusters
O) flat surface brightness profiles with substructures
O) Fornax is a great target for indirect DM studies because the relative
 low flux from CRps and high flux from DM
O) the IC upscattered photons from stars and dust are dominated in the
 relevant energy regimes by the continuum emission for our DM
 benchmark models
O) Fermi 3 year data will constrain the smallest mass of substructures
 using the benchmark models
O) difficult to detect DM without a Sommerfeld boost with Cherenkov
 telescopes since the boost from substructures is extended while the
 sensitivity of Cherenkov telescopes drops linearly with radius
 outside the point spread function (CHECK)
O) we rule out the leptophilic models in present form in 14 clusters,
 and limit the boost from Sommerfeld enhancement in the MW to less
 than 10
--) the tightest limits on DM and CRps from Fermi are in the 1-10 GeV
 regime, where Fornax, M49, and NGC4636 are the most constraining
 "clusters" for the DM and Virgo, Coma and Norma are very close to the
 predictions for the CRps
O) we provide a rather simple model to calculate the spatial and spectral
 distribution of dust and stars in cluster (might be used for
 galaxies? with different spatial profile)
}

@@

\clearpage
\appendix

{\it Spatial distribution -- stars and dust}\\ Our goal in this
section is to derive a simple spatial model for the distribution of SD
in galaxy clusters. For this reason we use stacked cluster
observations by Sloan in the $r$-band that trace the stars. We assume
that the dust trace the stars in the clusters, which should be
accurate to the order of magnitude estimate that we are interested in
here. The stacked surface brightness profiles in
\cite{2005MNRAS.358..949Z} are measured at redshift $z \sim 0.25$ with
an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
profiles are build up out of three components; diffuse intracluster
light (ICL), galaxies, and the brightest cluster galaxy (BCG) in the
center of clusters. However, the total volume overlap of the ISM to
the cluster is very small compared to the ICL- and BCG overlap with
the cluster, thus the relative contribution of the galaxies to the IC
emission is suppressed. To remove this bias we cut out the galaxies
that have been smoothed over the cluster in the stacked analysis. In
Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
as well as the fitted profiles\footnote{The measured brightness is
  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
  where the sun's absolute magnitude in the $r$-band is given by
  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
  luminosity of the sun by $L_\odot=3.85\,10^{33}
  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
normalized area to resembele the expected luminosity at radius
$r$. Our benchmark spatial model is shown with the solid black line,
and include the contribution from the ICL and BCG.

@@

{\it Spectral distribution -- stars and dust} \\ Our goal in this
section is to derive a simple spectral model for SD in galaxy
clusters. Since the radiation from galaxies are expected to leak out
into the ICM, we expect similar spectral distributions, at least to
the order of magnitude that we are interested in here. Hence, we use
the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a MW
type galaxy to characterize the spectral distribution of light from SD
in a cluster. Note, however, that we only keep the spectral shape, and
renormalize the spectral distribution using the luminosity from SD.

@@

{\it Normalization}\\ The spatial and spectral distribution functions
of the light from SD in a cluster are both normalized with a constant
determined from the luminosity in each respective wavelength. The
specific energy density is given by
\begin{eqnarray} 
u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
\end{eqnarray}
where we fix the unitless normalization $N_i(\lx)$ using the total
energy of the light in SD  within $\rvir$:
\begin{eqnarray} 
  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
 \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
\label{eq:E_SD}
\end{eqnarray}
Here we approximate the total energy of the photons within $\rvir$
($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
times the typical timescale it takes for a photon to propagate through
the cluster (we assume that the cluster is optically thin). Once we
derived the SD luminosities for a well representative cluster, we use
a IR to X-ray scaling relation to estimate the luminosity from an
arbitrary cluster:
\begin{equation}
L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
\label{eq:SD-X}
\end{equation}
where $\lx$ is the luminosity of the X-ray emitting gas within
$\rvir$.

@@

{\it Energy density}\\ The spatial distribution of the SD energy
density is an important quantity since it impacts the steady state
electron and positron spectra through cooling. A higher density of SD
in a cluster suppresses the spectra of the upscattering particles. With
the formalism presented above, we can now derive the energy density
from starlight and dust in a galaxy cluster through
\begin{eqnarray}
\label{eq:U_SD}
u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
\nonumber \\
&=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
\end{eqnarray}
In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
different radiation fields in a galaxy cluster with the mass
$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
SD energy density, where the total profile includes the contribution
from the ICL, the BCG and all the galaxies, while the galaxies are
excluded in the smooth profile. We find that even for a cluster with a
relative small mass the energy density of the SD components dominates
over the CMB and the magnetic fields (with a central B field of 3~$\mu
G$) within about 10\% of $\rvir$. Outside this radius the CMB is
dominating the energy density of the cluster, hence the magnetic
fields are always subdominant in the cluster and can safely be removed
from cluster IC calculations for a reasonable central B-field and
spectral index. Note that in this work we keep the contribution
from B-fields to the total energy density for consistency.

@@

@@

>>>>

Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray flux with
predictions of DM annihilation fluxes in the leptophilic and benchmark models.
To obtain the $\gamma$-ray fluxes, we scale the virial mass of clusters in the
extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our scaling
relations of Equations~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}). In
Figure~\ref{fig14}, we compare only those clusters of the HIFLUGCS sample with
Fermi limits to our predictions and show the DM flux predictions of the entire
sample in Fig.~\ref{fig21}.  We assume a boost factor due to substructures that
has a constant contribution per decade in substructure mass and has a mass
spectrum extending down to Earth masses. Fermi limits rule out the leptophilic
models in their present form with the mentioned assumptions in 14 clusters, and
limit the boost from Sommerfeld enhancement to less than 4 [?] in
Fornax. Assuming universality, this limits the Sommerfeld boost in the MW to
less than 10 (see Fig.~\ref{fig:boost_const}).  The flux level of the Fermi
limits are an indirect measure of the ambient background flux in the
$\gamma$-ray sky and/or the presence of strong point sources such as AGN in the
immediate vicinity of the cluster position. Hence, the ratio of the Fermi upper
limits to the predicted annihilation fluxes,
$F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good indication of the best cluster
candidates for indirect DM experiments. We identify Fornax, M49, NGC4636, and
Virgo to be prime candidates. Note however, that Virgo extends of $7\deg$ over
the sky which implies a lower surface brightness and lower signal-to-noise.
Fermi limits on individual clusters are expected to improve as $\sqrt{T/1.5
  \mathrm{yr}}$, where $T$ is the total elapsed time of the Fermi mission. We
emphasize that the very inhomogeneous distribution of $F_{\mathrm{UL}}/
F_{\mathrm{scal}}$ makes it unlikely to dramatically improve the limits through
a stacking analysis as the weak signal will dilute the average constraints.
Assuming the projected sensitivity of the future Cherenkov telescope array (CTA)
of [ANDERS: value?], we note that it will be difficult to detect the DM
annihilation signal from clusters without a Sommerfeld boost by Cherenkov
telescopes. This is because the boost from substructures is extended while the
sensitivity of Cherenkov telescopes drops linearly with radius outside the point
spread function.

@@

In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the flux
predictions by the semi-analytical Pinzke and Pfrommer model
\cite{2010MNRAS.409..449P} for CRp induced $\gamma$-rays that uses the
X-ray-inferred density profiles of clusters as an input. For consistency, we use
beta-model fits to ROSAT data of X-ray bright clusters for our $\gamma$-ray flux
estimates \cite{2002ApJ...567..71}). Hence these predictions are superior to
those that use luminosity-mass scaling relation to infer the expected
$\gamma$-ray flux---a method used by reference \cite{2010ApJ...717L..71A} to
compare to Fermi limits.  In this semi-analytic model, we employ the fact that
CRs accelerated at structure formation shocks and transported over cosmic time
exhibit a universal spectral form and an almost universal spatial
distribution. Depending on whether or not we account for the bias of
``artificial galaxies'' in cosmological simulations, we derive an optimistic or
conservative limit of the expected $\gamma$-ray emission from decaying pions
(bracketing our ignorance of the contribution of cluster galaxies to the overall
$\gamma$-ray flux from a cluster). Note that both models assume the maximally
allowed acceleration efficiency for strong shocks that transfer 50\% of the
shock kinetic energy to CRs and most likely will have to be corrected down if
this number is not realized at structure formation shocks. Secondly, these
simulations neglect active CR transport such as streaming and diffusion relative
to the gas, i.e. we assume that advective transport is the dominant one and CRs
are tightly coupled to the gas via flux-frozen magnetic fields tangled on
sufficiently small scales. Evidence from the statistics of radio halos suggests
that this might not be the case for relaxed clusters, arguing that CR streaming
in those objects could be responsible for a decrease in the central CR number
density. This effect would also reduce the expected $\gamma$-ray flux by up to a
factor of five \cite{2011A&A...527A..99E}. We note that the tightest Fermi
limits are obtained in the 1-10 GeV regime due to the largest effective area of
LAT there. In this energy band, the Fermi limits come close to the flux
predictions of Virgo, Coma and Norma. Using integrated flux limits from Fermi,
we arrive at very similar results.  We emphasize that by using our semi-analytic
modeling, the slight discrepancy of the scaling relation-based prediction with
the Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
seems to be less bright than an average cluster of the same mass as Norma. The
insenstitive limit on Perseus comes about since the central AGN in NGC1275 has
turned on over the last years, making it hard to determine a comparable
limit as obtained from the other clusters.

\begin{figure*}%[t]
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
 \caption{\it Comparison of the gamma-ray flux induced by CRps for the 106
   clusters included in the extended HIFLUGCS catalogue. The fluxes are
   calculated within $\rvir$, and are derived using a single beta profile for
   each cluster's gas density profile as obtained by ROSAT X-ray
   observations. The CR distribution follows the semi-analytically model derived
   by hydrodynamical cosmological cluster simulations \cite{2010MNRAS.409..449P}
   (see text for details). The upper panel shows the energy integrated flux
   above 100~MeV (left side) and above 100~GeV (right side), both as a function
   of HIFLUGCS cluster ID. The eight brightest clusters are labelled. The lower
   panel shows the relative difference between the $\gamma$-ray flux predicted by
   the mass-luminosity scaling relation and to the flux computed using the
   semi-analytical model \cite{2010MNRAS.409..449P}. The name of the clusters
   with the largest positive offset are printed out; as expected, they all
   correspond to cool core clusters.}
 \label{fig19}
\end{minipage}
\end{figure*}

To complete this section

@@

@@

@@

\appendix

\section{Detailed modelling of  starlight and dust in clusters}

\subsection{Radial profiles}

Our goal in this section is to derive a simple spatial model for the
distribution of SD in galaxy clusters. For this reason we use stacked cluster
observations by Sloan in the $r$-band that trace the stars. We assume that the
dust trace the stars in the clusters, which should be accurate to the order of
magnitude estimate that we are interested in here. The stacked surface
brightness profiles in \cite{2005MNRAS.358..949Z} are measured at redshift $z
\sim 0.25$ with an average mass of the clusters of
$4.0\times10^{13}\,\msun$. The profiles are build up out of three components;
diffuse intracluster light (ICL), galaxies, and the brightest cluster galaxy
(BCG) in the center of clusters. However, the total volume overlap of the ISM to
the cluster is very small compared to the ICL- and BCG overlap with the cluster,
thus the relative contribution of the galaxies to the IC emission is
suppressed. To remove this bias we cut out the galaxies that have been smoothed
over the cluster in the stacked analysis. In Fig.~\ref{fig:SD_spatial} we show
the SDSS stacked brightness profiles as well as the fitted profiles\footnote{The
  measured brightness is converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$, where
  the sun's absolute magnitude in the $r$-band is given by
  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the luminosity of the
  sun by $L_\odot=3.85\,10^{33} \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the
unitless $\rvir$ normalized area to resembele the expected luminosity at radius
$r$. Our benchmark spatial model is shown with the solid black line, and include
the contribution from the ICL and BCG.

@@

\subsection{Energy spectrum}

Our goal in this section is to derive a simple spectral model for SD in galaxy
clusters. Since the radiation from galaxies are expected to leak out into the
ICM, we expect similar spectral distributions, at least to the order of
magnitude that we are interested in here. Hence, we use the IR to UV spectrum
derived in \cite{2006ApJ...648L..29P} for a MW type galaxy to characterize the
spectral distribution of light from SD in a cluster. Note, however, that we only
keep the spectral shape, and renormalize the spectral distribution using the
luminosity from SD.

@@

The spatial and spectral distribution functions
of the light from SD in a cluster are both normalized with a constant
determined from the luminosity in each respective wavelength. The
specific energy density is given by
\begin{eqnarray} 
u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
\end{eqnarray}
where we fix the unitless normalization $N_i(\lx)$ using the total
energy of the light in SD  within $\rvir$:
\begin{eqnarray} 
  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
 \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
\label{eq:E_SD}
\end{eqnarray}
Here we approximate the total energy of the photons within $\rvir$
($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
times the typical timescale it takes for a photon to propagate through
the cluster (we assume that the cluster is optically thin). Once we
derived the SD luminosities for a well representative cluster, we use
a IR to X-ray scaling relation to estimate the luminosity from an
arbitrary cluster:
\begin{equation}
L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
\label{eq:SD-X}
\end{equation}
where $\lx$ is the luminosity of the X-ray emitting gas within
$\rvir$.

@@

The spatial distribution of the SD energy density is an important quantity since
it impacts the steady state electron and positron spectra through cooling. A
higher density of SD in a cluster suppresses the spectra of the upscattering
particles. With the formalism presented above, we can now derive the energy
density from starlight and dust in a galaxy cluster through
\begin{eqnarray}
\label{eq:U_SD}
u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
\nonumber \\
&=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
\end{eqnarray}
In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
different radiation fields in a galaxy cluster with the mass
$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
SD energy density, where the total profile includes the contribution
from the ICL, the BCG and all the galaxies, while the galaxies are
excluded in the smooth profile. We find that even for a cluster with a
relative small mass the energy density of the SD components dominates
over the CMB and the magnetic fields (with a central B field of 3~$\mu
G$) within about 10\% of $\rvir$. Outside this radius the CMB is
dominating the energy density of the cluster, hence the magnetic
fields are always subdominant in the cluster and can safely be removed
from cluster IC calculations for a reasonable central B-field and
spectral index. Note that in this work we keep the contribution
from B-fields to the total energy density for consistency.

@@

\section{Source functions of different DM models}

@@

\section{Gas density profile of Fornax}
